# Results

## Copular constructions

```{r data, include=F}
data_df <- read_csv(here("data", "data.csv")) #, locale = locale(encoding = "UTF-16LE"))
questions <- read_csv(here("data", "questions.csv"))

data_tib <- data_df |> 
  filter(Finished == "TRUE") |> 
  pivot_longer(cols = Q3_1:Q11_24, names_to = "question") |> 
  filter(!is.na(value)) |> 
  left_join(questions, by = "question") |> 
  mutate(q_type = q_type |> as.factor(),
         lang_group = lang_group |> as.factor(),
         value = value |> as.numeric(),
         proficiency = Q18 |> as.numeric())
```

```{r copula}
cop <- data_tib |> 
  filter(lang_group != 'O',
         test_phen == 1) |> 
  mutate(cop_type = cop_type |> as.factor() |> 
           fct_shift(1) |> `contrasts<-`(value = contr.sum(3) * 0.5),
         q_type = q_type |> fct_drop() |> `contrasts<-`(value = contr.sum(2) * 0.5),
         lang_group = lang_group |> fct_drop() |> `contrasts<-`(value = contr.sum(2) * 0.5))

cop_lm <- lmer(value ~ cop_type * q_type * lang_group + 
                 (1 | ResponseId) + (1 | s_label),
               data = cop)

cop_sum <- cop_lm |> tidy()
```

(ref:cop-plot) Distributions of ratings for copular constructions by complement type, sentence version, and MT. Black dashed lines indicate means. C: Chinese; M: Malay.
```{r cop-plot, out.width="100%", fig.cap="(ref:cop-plot)"}
cop_mean <- cop |> 
  group_by(cop_type, s_variant) |> 
  summarise(mean = mean(value),
            sd = sd(value),
            count = n()) |> 
  mutate(se = sd / sqrt(count),
         lower_ci = mean - se,
         upper_ci = mean + se)

cop_lab <- labeller(
  s_variant = c("a" = "With copula", "b" = "Without copula"), 
  cop_type = c(`1` = "NP", `2` = "AP", `3` = "PP"))

cop_plot <- ggplot(data = cop |> mutate(cop_type = cop_type |> 
                              fct_relevel(c("1", "2", "3")))) +
  geom_bar(aes(x = value, fill = lang_group), stat = "count") +
  geom_vline(aes(xintercept = mean), data = cop_mean, lty = "dashed") +
  facet_grid(cop_type ~ s_variant, labeller = cop_lab) +
  labs(x = "Rating", y = "Count") +
  scale_fill_brewer(palette = "Set2", name = "MT")

cop_plot
```

```{r cop_stats}
cop_sw <- cop_lm |> compute_redres() |> shapiro.test()
cop_emm_qt <- emmeans(cop_lm, ~ q_type) |> tidy()
cop_emm_cqt <- emmeans(cop_lm, ~ cop_type | q_type)
cop_con_cqt <- contrast(cop_emm_cqt, method = "pairwise") |> tidy()
cop_emm_cqt <- cop_emm_cqt |> tidy()
cop_emm_lg <- emmeans(cop_lm, ~ lang_group) |> tidy()
```

Participants' ratings for items involving copular constructions are shown in Figure \@ref(fig:cop-plot).
We conducted a linear regression with rating as the outcome variable, and complement type, sentence version, and MT as fixed effects with sum contrasts, along with all interactions. 
We also included participant and item as random effects.
The full model specification is as follows: `rating ~ comp_type * sent_version * mt + (1 | ppt_id) + (1 | item_id)`.[^03-01]

[^03-01]: A Shapiro--Wilk test revealed that residuals of the linear regression were not normally distributed ($W =$ `r cop_sw$statistic`, $p < .001$). 
However, visual observation of the Q--Q plot suggested that the deviation was minor and only occurred near the top tail of the distribution, which was expected due to negative skew (`r skewness(cop$value)`) associated with a ceiling effect. 
As such, linear regression remained the analysis of choice.
```{r cop-resqq}
cop_resqq <- plot_resqq(cop_lm)
```

Model results suggested that there was an unsurprising main effect of sentence version ($b =$ `r cop_sum |> filter(term == "q_type1") |> pull(estimate)`, $p$ `r cop_sum |> filter(term == "q_type1") |> pull(p.value) |> printp()`), with sentences including the copula having higher mean ratings (`r cop_emm_qt |> filter(q_type == 1) |> pull(estimate)` $\pm$ `r cop_emm_qt |> filter(q_type == 1) |> pull(std.error)`) than sentences without the copula (`r cop_emm_qt |> filter(q_type == 2) |> pull(estimate)` $\pm$ `r cop_emm_qt |> filter(q_type == 2) |> pull(std.error)`).[^03-02]

[^03-02]: Reported values indicate estimated marginal means and their 95% confidence intervals.

There was no main effect of MT ($b =$ `r cop_sum |> filter(term == "lang_group1") |> pull(estimate)`, $p =$ `r cop_sum |> filter(term == "lang_group1") |> pull(p.value) |> printp()`), suggesting that mean ratings did not differ between Chinese speakers (`r cop_emm_lg |> filter(lang_group == "C") |> pull(estimate)` $\pm$ `r cop_emm_lg |> filter(lang_group == "C") |> pull(std.error)`) and Malay speakers (`r cop_emm_lg |> filter(lang_group == "M") |> pull(estimate)` $\pm$ `r cop_emm_lg |> filter(lang_group == "C") |> pull(std.error)`).

However, there were interaction effects between complement type and question type, as shown in Figure \@ref(fig:cop-pairwise). 
Post-hoc pairwise comparisons using the Tukey method revealed that there were no significant pairwise contrasts for sentences including the copula (all $p >$ `r cop_con_cqt |> filter(q_type == 1) |> pull(adj.p.value) |> min() |> floor_dec(1)`). 
However, there were significant pairwise contrasts for sentences without the copula.
Sentences with a PP complement (`r cop_emm_cqt |> filter(q_type == 2, cop_type == 3) |> pull(estimate)` $\pm$ `r cop_emm_cqt |> filter(q_type == 2, cop_type == 3) |> pull(std.error)`) had higher ratings than sentences with an NP complement (`r cop_emm_cqt |> filter(q_type == 2, cop_type == 1) |> pull(estimate)` $\pm$ `r cop_emm_cqt |> filter(q_type == 2, cop_type == 1) |> pull(std.error)`, $b =$ `r cop_con_cqt |> filter(q_type == 2, contrast == "cop_type2 - cop_type3") |> pull(estimate) |> abs()`, $p =$ `r cop_con_cqt |> filter(q_type == 2, contrast == "cop_type2 - cop_type3") |> pull(adj.p.value) |> printp()`) and also had higher ratings than sentences with an AP complement (`r cop_emm_cqt |> filter(q_type == 2, cop_type == 2) |> pull(estimate)` $\pm$ `r cop_emm_cqt |> filter(q_type == 2, cop_type == 2) |> pull(std.error)`, $b =$ `r cop_con_cqt |> filter(q_type == 2, contrast == "cop_type3 - cop_type1") |> pull(estimate) |> abs()`, $p =$ `r cop_con_cqt |> filter(q_type == 2, contrast == "cop_type3 - cop_type1") |> pull(adj.p.value) |> printp()`). 
Ratings for sentences with an NP complement were not significantly different from sentences with an AP complement ($b =$ `r cop_con_cqt |> filter(q_type == 2, contrast == "cop_type2 - cop_type1") |> pull(estimate) |> abs()`, $p =$ `r cop_con_cqt |> filter(q_type == 2, contrast == "cop_type2 - cop_type1") |> pull(adj.p.value) |> printp()`).

(ref:cop-pw) Mean ratings for copular constructions by complement type and sentence version. \*: $p < .05$, \*\*: $p < .01$.
```{r cop-pairwise, out.width="100%", fig.cap="(ref:cop-pw)"}
cop_emm <- emmeans(cop_lm, ~ cop_type | q_type)
cop_con <- contrast(cop_emm, method = "pairwise", adjust = "tukey") |> 
  as_tibble() |>
  separate(contrast, c("g1", "g2"), " - ") |> 
  mutate(group1 = pmin(g1, g2),
         group2 = pmax(g1, g2),
         p.signif = cut(p.value,
                        breaks = c(-Inf, .0001, .001, .01, .05, .1, 1),
                        labels = c("****", "***", "**", "*", "ns", "ns"))) |> 
  select(-g1, -g2) |> 
  arrange(q_type, group2) |> 
  add_x_position(x = "cop_type", 
                 group = "q_type", 
                 dodge = 0.9)

cop_pw <- ggplot(data = cop_mean |> mutate(cop_type = cop_type |> 
                                             fct_relevel(c("1", "2", "3")) |> 
                                             fct_recode("NP" = "1", 
                                                        "AP" = "2",
                                                        "PP" = "3"))) +
  geom_col(aes(y = mean, x = cop_type, fill = s_variant),
           position = position_dodge()) +
  geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci, 
                    x = cop_type, group = s_variant),
                width = 0.3,
                position = position_dodge(width = 0.9)) +
  stat_pvalue_manual(cop_con,
                     y.position = 1.1 * max(cop_mean$mean),
                     step.increase = 0.2,
                     tip.length = 0.03,
                     hide.ns = T) +
  labs(x = "Complement type", y = "Mean rating") +
  scale_fill_manual(name = "Sentence type",
                    labels = c("With copula", "Without copula"),
                    values = c("gold", "cornflowerblue"))

cop_pw
```

Surprisingly, there were no interaction effects involving MT. 
There was no interaction between language and complement type ($p >$ `r cop_sum |> filter(grepl("cop_type[12]:lang_group1$", term)) |> pull(p.value) |> min() |> floor_dec(1)`), or language and sentence version ($p =$ `r cop_sum |> filter(term == "q_type1:lang_group1") |> pull(p.value) |> printp()`), or language and both complement type and sentence version ($p >$ `r cop_sum |> filter(grepl("cop_type[12]:q_type1:lang_group1$", term)) |> pull(p.value) |> min() |> floor_dec(1)`).

## Past tense marking---past marking type

```{r past}
past <- data_tib |> 
  filter(lang_group != 'O',
         test_phen == 2) |> 
  mutate(past_type = past_type |> as.factor() |> 
           fct_shift(1) |> `contrasts<-`(value = contr.sum(5) * 0.5),
         q_type = q_type |> fct_drop() |> `contrasts<-`(value = contr.sum(2) * 0.5),
         lang_group = lang_group |> fct_drop() |> `contrasts<-`(value = contr.sum(2) * 0.5))

past_lm <- lmer(value ~ past_type * q_type * lang_group + 
                 (1 | ResponseId) + (1 | s_label),
               data = past)

past_sum <- past_lm |> tidy()
```

(ref:past-plot) Distributions of ratings for past tense constructions by past tense marker, sentence version, and MT. Black dashed lines indicate means. C: Chinese; M: Malay.
```{r past-plot, out.width="100%", fig.cap="(ref:past-plot)"}
past_mean <- past |> 
  group_by(past_type, s_variant) |> 
  summarise(mean = mean(value),
            sd = sd(value),
            count = n()) |> 
  mutate(se = sd / sqrt(count),
         lower_ci = mean - se,
         upper_ci = mean + se)

past_lab <- labeller(
  s_variant = c("a" = "With past marking", "b" = "Without past marking"), 
  past_type = c(`1` = "Suppletion", `2` = "Vowel", `3` = "[t]/[d]",
                `4` = "[ɪd]", `5` = "Vwl + [t]/[d]"))

past_plot <- ggplot(data = past |> mutate(past_type = past_type |> 
                               fct_relevel(c("1", "5", "2", "4", "3")))) +
  geom_bar(aes(x = value, fill = lang_group), stat = "count") +
  geom_vline(aes(xintercept = mean), data = past_mean, lty = "dashed") +
  facet_grid(past_type ~ s_variant, labeller = past_lab) +
  labs(x = "Rating", y = "Count") +
  scale_fill_brewer(palette = "Set2", name = "MT")

past_plot
```

```{r past_stats}
past_sw <- past_lm |> compute_redres() |> shapiro.test()
past_emm_qt <- emmeans(past_lm, ~ q_type) |> tidy()
past_emm_lqt <- emmeans(past_lm, ~ lang_group | q_type)
past_con_lqt <- contrast(past_emm_lqt, method = "pairwise") |> tidy()
past_emm_lg <- emmeans(past_lm, ~ lang_group) |> tidy()
```

Participants' ratings for items involving past tense constructions are shown in Figure \@ref(fig:past-plot). 
We conducted a linear regression with rating as the outcome variable, and past marking type, sentence version, and MT as fixed effects with sum contrasts, along with all interactions. 
We also included participant and item as random effects.
The full model specification is as follows: `rating ~ past_type * sent_version * mt + (1 | ppt_id) + (1 | item_id)`.[^03-03]

[^03-03]: Similar to the ratings for copular constructions, a Shapiro--Wilk test revealed that residuals of the linear regression were not normally distributed ($W =$ `r past_sw$statistic`, $p < .001$). 
Again, visual observation of the Q--Q plot suggested that the deviation was minor and only occurred near the top tail of the distribution, which was expected due to negative skew (`r skewness(past$value)`) associated with a ceiling effect. 
As such, linear regression remained the analysis of choice.
```{r past-resqq}
past_resqq <- plot_resqq(past_lm)
```

Model results suggested that there was again a main effect of sentence version ($b =$ `r past_sum |> filter(term == "q_type1") |> pull(estimate)`, $p$ `r past_sum |> filter(term == "q_type1") |> pull(p.value) |> printp()`), with sentences including the copula having higher mean ratings (`r past_emm_qt |> filter(q_type == 1) |> pull(estimate)` $\pm$ `r past_emm_qt |> filter(q_type == 1) |> pull(std.error)`) than sentences without the copula (`r past_emm_qt |> filter(q_type == 2) |> pull(estimate)` $\pm$ `r past_emm_qt |> filter(q_type == 2) |> pull(std.error)`).

There was again no main effect of MT ($b =$ `r past_sum |> filter(term == "lang_group1") |> pull(estimate)`, $p =$ `r past_sum |> filter(term == "lang_group1") |> pull(p.value) |> printp()`), suggesting that mean ratings did not differ between Chinese speakers (`r past_emm_lg |> filter(lang_group == "C") |> pull(estimate)` $\pm$ `r past_emm_lg |> filter(lang_group == "C") |> pull(std.error)`) and Malay speakers (`r past_emm_lg |> filter(lang_group == "M") |> pull(estimate)` $\pm$ `r past_emm_lg |> filter(lang_group == "C") |> pull(std.error)`).

In contrast with the pattern of results for copular constructions, there were no significant interaction effects between past marking type and sentence version (all $p >$ `r past_sum |> filter(grepl("past_type[1-4]:q_type1$", term)) |> pull(p.value) |> min() |> floor_dec(2)`).
There were also no significant interaction effects between past marking type and both question type and MT (all $p >$ `r past_sum |> filter(grepl("past_type[1-4]:q_type1:", term)) |> pull(p.value) |> min() |> floor_dec(2)`).

Conversely, there was a significant interaction effect between sentence version and MT ($b =$ `r past_sum |> filter(term == "q_type1:lang_group1") |> pull(estimate)`, $p =$ `r past_sum |> filter(term == "q_type1:lang_group1") |> pull(p.value) |> printp()`), as shown in Figure \@ref(fig:past-pw). 
Post-hoc pairwise comparisons using the Tukey method did not reveal any simple effects of MT (all $p >$ `r past_con_lqt |> pull(p.value) |> min() |> floor_dec(1)`), suggesting that Chinese and Malay speakers did not differ in their ratings for either sentence version, although they differed in the _difference_ in ratings between sentences with and without past tense marking. 

(ref:past-pw) Mean ratings for past tense constructions by MT and sentence version. C: Chinese; M: Malay.
```{r past-pw, out.width="100%", fig.cap="(ref:past-pw)"}
past_mean <- past |> 
  group_by(lang_group, s_variant) |> 
  summarise(mean = mean(value),
            sd = sd(value),
            count = n()) |> 
  mutate(se = sd / sqrt(count),
         lower_ci = mean - se,
         upper_ci = mean + se)

past_lm <- lmer(value ~ q_type * lang_group + 
                    (1 | ResponseId) + (1 | s_label),
                  data = past)
past_emm <- emmeans(past_lm, ~ lang_group | q_type)
past_con <- contrast(past_emm, method = "pairwise") |> 
  as_tibble() |>
  separate(contrast, c("group1", "group2"), " - ") |> 
  mutate(p.signif = cut(p.value,
                        breaks = c(-Inf, .0001, .001, .01, .05, .1, 1),
                        labels = c("****", "***", "**", "*", "ns", "ns"))) # |> 
  # arrange(q_type, group2)# |> 
  #add_x_position(x = "past_type", 
                 # group = "q_type", 
                 # dodge = 0.9)

past_pw <- ggplot(data = past_mean) +
  geom_col(aes(y = mean, x = lang_group, fill = s_variant),
           position = position_dodge()) +
  geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci, 
                    x = lang_group, group = s_variant),
                width = 0.3,
                position = position_dodge(width = 0.9)) +
  stat_pvalue_manual(past_con,
                     y.position = 1.1 * max(past_mean$mean),
                     step.increase = 0.2,
                     tip.length = 0.03,
                     hide.ns = T) +
  labs(x = "Language group", y = "Mean rating") +
  scale_fill_manual(name = "Sentence type",
                    labels = c("With past marking", "Without past marking"),
                    values = c("gold", "cornflowerblue"))

past_pw
```

## Past tense marking---event aspect

As past marking type was not a significant predictor of ratings for sentences involving the past tense construction, we conducted an exploratory analysis to determine whether there were other possible predictors that would explain the variation observed in participants' responses to different past tense items.
One candidate was the aspect of the event semantics, which was noted by @hoDynamicsContactContinuum1993 also to influence the proportion of past marking.
Specifically, they found that verbs which were telic showed the highest proportion of past marking, followed by stative verbs, followed by atelic verbs.[^03-04] 
To explore the role of event semantics in past tense marking, we evaluated each sentence in terms of the aspectual features of the event described: dynamic or stative, durative or punctual, and telic or atelic [@dowtyWordMeaningMontague1979; @olsenSemanticsPragmaticsLexical1994; @vendlerVerbsTimes1957].
Using these features, we classified each sentence into aspectual classes: accomplishment ([+dynamic, +durative, +telic]), achievement ([+dynamic, $-$durative, +telic]), activity ([+dynamic, +durative, $-$telic]), or state ([$-$dynamic, +durative, $-$telic]).[^03-05] 
It is important to emphasise that this set of analyses is exploratory and post-hoc; as such, the number and order of presentation of sentences of different aspectual classes was not balanced within participants.
A histogram of the number of sentences of each aspectual class is shown in Figure \@ref(fig:past-sem-hist).

[^03-04]: Note that in @hoDynamicsContactContinuum1993, they used the terms "punctual" and "non-punctual", but in fact the criterion used to distinguish between these two categories is explicitly characterised as the former category having the feature [+telic] or [+completive].

[^03-05]: Other classes such as semelfactives ([+dynamic, $-$durative, $-$telic]) were not present among the sentences in our questionnaire.

(ref:past-sem-hist) Histogram of aspectual classes of past tense constructions.
```{r past-sem-hist, out.width="100%", fig.cap="(ref:past-sem-hist)"}
semantics <- read_csv(here("data", "past_semantics.csv"))
past_sem <- past |> 
  left_join(semantics |> select(question, dynamic, durative, telic, aspectual_class),
            by = "question") |> 
  mutate(aspectual_class = aspectual_class |> as.factor() |> `contrasts<-`(value = contr.sum(4) * 0.5))

past_sem_lm <- lmer(value ~ q_type * lang_group * aspectual_class + 
                 (1 | ResponseId) + (1 | s_label),
               data = past_sem)

past_sem_sum <- past_sem_lm |> tidy()

semantics_hist <- semantics |> 
  count(aspectual_class) |> 
  mutate(n = n / 2)

past_sem_hist <- ggplot(semantics_hist) +
  geom_col(aes(x = aspectual_class, y = n), fill = "mediumorchid") +
  scale_x_discrete(labels = c("Accomplishment", "Achievement", "Activity", "State")) +
  labs(x = "Event aspectual class", y = "Count")

past_sem_hist
```

Participants' ratings for past tense constructions by aspectual class are shown in Figure \@ref(fig:past-sem-plot).
We conducted a linear regression with rating as the outcome variable, and aspectual class, sentence version, and MT as fixed effects with sum contrasts, along with all interactions. 
We also included participant and item as random effects.
The full model specification is as follows: `rating ~ aspectual_class * sent_version * mt + (1 | ppt_id) + (1 | item_id)`.

(ref:past-sem-plot) Distributions of ratings for past tense constructions by event aspect, sentence version, and MT. Black dashed lines indicate means. C: Chinese; M: Malay.
```{r past-sem-plot, out.width="100%", fig.cap="(ref:past-sem-plot)"}
past_sem_mean <- past_sem |> 
  group_by(aspectual_class, s_variant) |> 
  summarise(mean = mean(value),
            sd = sd(value),
            count = n()) |> 
  mutate(se = sd / sqrt(count),
         lower_ci = mean - se,
         upper_ci = mean + se)

past_sem_prop <- past_sem |> 
  group_by(aspectual_class, s_variant, lang_group) |> 
  count(value) |> 
  ungroup(lang_group) |> 
  mutate(freq = n / sum(n))

past_sem_lab <- labeller(
  s_variant = c("a" = "With past marking", "b" = "Without past marking"), 
  aspectual_class = Hmisc::capitalize)

past_sem_plot <- ggplot(data = past_sem_prop) +
  geom_bar(aes(x = value, y = freq, fill = lang_group), stat = "identity") +
  geom_vline(aes(xintercept = mean), data = past_sem_mean, lty = "dashed") +
  facet_grid(aspectual_class ~ s_variant, labeller = past_sem_lab) +
  labs(x = "Rating", y = "Frequency") +
  scale_fill_brewer(palette = "Set2", name = "MT")

past_sem_plot
```

(ref:past-sem-pw) Mean ratings for past tense marking by event aspectual class and sentence version. \*: $p < .05$.
```{r past-sem-pairwise, out.width="100%", fig.cap="(ref:past-sem-pw)"}
past_sem_emm <- emmeans(past_sem_lm, ~ aspectual_class | q_type * lang_group)
past_sem_emm_tidy <- past_sem_emm |> tidy()
past_sem_con <- contrast(past_sem_emm, method = "pairwise", adjust = "tukey") |> 
  as_tibble() |>
  separate(contrast, c("g1", "g2"), " - ") |> 
  mutate(group1 = pmin(g1, g2),
         group2 = pmax(g1, g2),
         p.signif = cut(p.value,
                        breaks = c(-Inf, .0001, .001, .01, .05, .1, 1),
                        labels = c("****", "***", "**", "*", "ns", "ns"))) |> 
  select(-g1, -g2) |> 
  arrange(q_type, group2) |> 
  add_x_position(x = "aspectual_class", 
                 group = "q_type", 
                 dodge = 0.9)

past_sem_mean_2 <- past_sem |> 
  group_by(aspectual_class, s_variant, lang_group) |> 
  summarise(mean = mean(value),
            sd = sd(value),
            count = n()) |> 
  mutate(se = sd / sqrt(count),
         lower_ci = mean - se,
         upper_ci = mean + se)

past_sem_pw <- ggplot(data = past_sem_mean_2) +
  geom_col(aes(y = mean, x = aspectual_class, fill = s_variant),
           position = position_dodge()) +
  geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci, 
                    x = aspectual_class, group = s_variant),
                width = 0.3,
                position = position_dodge(width = 0.9)) +
  facet_grid(lang_group ~ .) +
  stat_pvalue_manual(past_sem_con,
                     y.position = 1.1 * max(past_sem_mean$mean),
                     step.increase = 0.2,
                     tip.length = 0.03,
                     hide.ns = T) +
  labs(x = "Event aspectual class", y = "Mean rating") +
  scale_fill_manual(name = "Sentence type",
                    labels = c("With past tense marking", "Without past tense marking"),
                    values = c("gold", "cornflowerblue")) +
  scale_x_discrete(labels = c("Accomplishment", "Achievement", "Activity", "State"))

past_sem_pw
```

Model results suggested that there was again a main effect of sentence version ($b =$ `r past_sem_sum |> filter(term == "q_type1") |> pull(estimate)`, $p$ `r past_sem_sum |> filter(term == "q_type1") |> pull(p.value) |> printp()`), and an interaction effect between sentence version and MT ($b =$ `r past_sem_sum |> filter(term == "q_type1:lang_group1") |> pull(estimate)`, $p =$ `r past_sem_sum |> filter(term == "q_type1:lang_group1") |> pull(p.value) |> printp()`).
Additionally, there was an interaction effect among sentence version, MT, and event aspectual class, as shown in Figure \@ref(fig:past-sem-pairwise). 
Post-hoc pairwise comparisons using the Tukey method revealed that there were no significant pairwise contrasts for sentences with past tense marking (all $p >$ `r past_sem_con |> filter(q_type == 1) |> pull(p.value) |> min() |> floor_dec(1)`). 
For sentences without past tense marking, there were no significant pairwise contrasts for Malay MT speakers (all $p >$ `r past_sem_con |> filter(q_type == 2, lang_group == "M") |> pull(p.value) |> min() |> floor_dec(1)`). 
However, for Chinese MT speakers, sentences that expressed unmarked past activities (`r past_sem_emm_tidy |> filter(q_type == 2, lang_group == "C", aspectual_class == "activity") |> pull(estimate)` $\pm$ `r past_sem_emm_tidy |> filter(q_type == 2, lang_group == "C", aspectual_class == "activity") |> pull(std.error)`) had higher ratings than sentences that expressed unmarked past states (`r past_sem_emm_tidy |> filter(q_type == 2, lang_group == "C", aspectual_class == "state") |> pull(estimate)` $\pm$ `r past_sem_emm_tidy |> filter(q_type == 2, lang_group == "C", aspectual_class == "state") |> pull(std.error)`, $b =$ `r past_sem_con |> filter(q_type == 2, lang_group == "C", group1 == "activity", group2 == "state") |> pull(estimate) |> abs()`, $p =$ `r past_sem_con |> filter(q_type == 2, lang_group == "C", group1 == "activity", group2 == "state") |> pull(p.value) |> printp()`). 

## Individual differences

To better understand the observed variation in responses, we conducted two further exploratory analyses.
The first analysis involved understanding the relationship in participants' responses to the two types of constructions studied: were participants who rated CSE copular constructions more highly also more likely to rate CSE past tense constructions more highly?
We calculated the mean and 95% confidence intervals for both types of CSE constructions for each participant, shown in Figure \@ref(fig:cor).

(ref:cor) Ratings for copula and past tense CSE constructions by participant. Error bars indicate 95% confidence intervals. Blue line and shaded area indicate the line of best fit and 95% confidence intervals.
```{r cor, out.width="100%", fig.cap="(ref:cor)"}
both <- data_tib |> 
  filter(lang_group != "O",
         q_type == 2) |> 
  group_by(ResponseId, test_phen) |> 
  summarise(avg_rating = mean(value),
            sd_rating = sd(value),
            n = n()) |> 
  mutate(se_rating = sd_rating / sqrt(n)) |> 
  select(-sd_rating, -n) |> 
  pivot_wider(names_from = test_phen,
              values_from = c(avg_rating, se_rating))

both_cor <- cor(both$avg_rating_1, both$avg_rating_2)

both_plot <- ggplot(both,
                    aes(x = avg_rating_1, y = avg_rating_2)) +
  geom_point() +
  geom_errorbar(aes(ymin = avg_rating_2 - 0.95*se_rating_2, 
                    ymax = avg_rating_2 + 0.95*se_rating_2),
                alpha = .5) +
  geom_errorbar(aes(xmin = avg_rating_1 - 0.95*se_rating_1, 
                    xmax = avg_rating_1 + 0.95*se_rating_1),
                alpha = .5) +
  geom_smooth(method = "lm") +
  geom_abline(slope = 1, intercept = 0, lty = "dashed") +
  labs(x = "Copular construction rating",
       y = "Past tense construction rating")

both_plot
```

The correlation in means between the two types of CSE constructions was moderate, $r =$ `r both_cor`, suggesting that participants sometimes (but not always) endorsed both types of CSE constructions with similar ratings.
Additionally, many of the points lay above the $y = x$ line, suggesting that participants generally rated the CSE past tense constructions higher than the CSE copular constructions; this aligns with findings from @leimgruberSingaporeEnglishStructure2013, who identified that lack of verbal inflection as being more common than zero copula.

The second analysis studied the relationship between participants' ratings and their self-assessed MT language proficiency.
A histogram of participants' MT proficiencies is shown in Figure \@ref(fig:prof-hist).

(ref:prof-hist) Histogram of participants' self-assessed MT language proficiency by MT. C: Chinese; M: Malay.
```{r prof-hist, out.width="100%", fig.cap="(ref:prof-hist)"}
ppts <- data_tib |> 
  filter(lang_group != "O") |> 
  select(ResponseId, lang_group, proficiency) |> 
  distinct()

prof_hist <- ggplot(ppts, aes(x = proficiency)) + 
  geom_bar(aes(fill = lang_group), position = "dodge") +
  scale_fill_brewer(palette = "Set2", name = "MT") +
  labs(x = "MT proficiency",
       y = "Number of participants")

prof_hist
```

As the sample size did not support running a full statistical model with all levels of interaction, we omitted copula or past tense type as predictors, and instead ran a single joint model on both constructions.
We conducted a linear regression with rating as the outcome variable, and construction, sentence version, MT, and MT proficiency as fixed effects, along with all interactions. 
Construction, sentence version, and MT were coded with sum contrasts, and MT proficiency was standardised. 
We also included participant and item as random effects.
The full model specification is as follows: `rating ~ construction * sent_version * mt * proficiency + (1 | ppt_id) + (1 | item_id)`.

```{r prof}
by_prof <- data_tib |> 
  filter(lang_group != "O",
         test_phen %in% c(1, 2)) |> 
  mutate(test_phen = test_phen |> as.factor() |> `contrasts<-`(value = contr.sum(2) * 0.5),
         q_type = q_type |> fct_drop() |> `contrasts<-`(value = contr.sum(2) * 0.5),
         lang_group = lang_group |> fct_drop() |> `contrasts<-`(value = contr.sum(2) * 0.5),
         proficiency_std = proficiency |> scale())

prof_lm <- lmer(value ~ test_phen * q_type * lang_group * proficiency_std + 
          (1 | ResponseId) + (1 | s_label),
      data = by_prof)

prof_sum <- prof_lm |> tidy()
```

(ref:prof-plot) Ratings for copula and past tense constructions by participants' self-assessed MT language proficiency, sentence version, and MT. C: Chinese; M: Malay.
```{r prof-plot, out.width="100%", fig.cap="(ref:prof-plot)"}
phen_labeller <- function(value) {
  phen <- list("1" = "Copula", "2" = "Past tense")
  return(phen[value])
}

prof_plot <- ggplot(by_prof, aes(x = proficiency, y = value)) + 
  geom_jitter(aes(shape = q_type, col = lang_group), alpha = .4) + 
  geom_smooth(aes(lty = q_type, col = lang_group), method = "lm") +
  scale_color_brewer(palette = "Set2", name = "MT") +
  scale_linetype_discrete(labels = c("SSE", "CSE")) +
  scale_shape_discrete(labels = c("SSE", "CSE")) +
  facet_grid(~ test_phen, labeller = labeller(test_phen = phen_labeller)) +
  labs(x = "MT proficiency",
       y = "Rating",
       linetype = "Sentence version",
       shape = "Sentence version")

prof_plot
```

```{r prof-pairwise}
prof_emm <- emtrends(prof_lm, ~ q_type, var = "proficiency_std") |> 
  tidy()
prof_int_emm <- emtrends(prof_lm, ~ q_type * lang_group, var = "proficiency_std") |> 
  tidy()
```

Participants' ratings by their self-assessed MT proficiency are shown in Figure \@ref(fig:prof-plot).
We focus on model results specifically related to MT proficiency, as other results were similar to results reported in the previous sections.
There was an interaction effect between sentence version and MT proficiency ($b =$ `r prof_sum |> filter(term == "q_type1:proficiency_std") |> pull(estimate)`, $p =$ `r prof_sum |> filter(term == "q_type1:proficiency_std") |> pull(p.value) |> printp()`), with the estimated marginal trend of MT proficiency being negative for SSE sentences ($b =$ `r prof_emm |> filter(q_type == 1) |> pull(proficiency_std.trend)`) and positive for CSE sentences ($b =$ `r prof_emm |> filter(q_type == 2) |> pull(proficiency_std.trend)`), although neither reached significance (all $p >$ `r prof_emm |> pull(p.value) |> min() |> floor_dec(1)`).

There was also an interaction effect among sentence version, MT, and MT proficiency ($b =$ `r prof_sum |> filter(term == "q_type1:lang_group1:proficiency_std") |> pull(estimate)`, $p =$ `r prof_sum |> filter(term == "q_type1:lang_group1:proficiency_std") |> pull(p.value) |> printp()`). 
For Chinese MT speakers, the estimated marginal trend of MT proficiency was positive for both SSE ($b =$ `r prof_int_emm |> filter(q_type == 1, lang_group == "C") |> pull(proficiency_std.trend)`) and CSE ($b =$ `r prof_int_emm |> filter(q_type == 2, lang_group == "C") |> pull(proficiency_std.trend)`) sentences, whereas for Malay MT speakers, the estimated marginal trend of MT proficiency was negative for SSE sentences ($b =$ `r prof_int_emm |> filter(q_type == 1, lang_group == "M") |> pull(proficiency_std.trend)`) but positive for CSE sentences ($b =$ `r prof_int_emm |> filter(q_type == 2, lang_group == "M") |> pull(proficiency_std.trend)`).
Only the negative SSE trend for Malay MT speakers reached significance ($p =$ `r prof_int_emm |> filter(q_type == 1, lang_group == "M") |> pull(p.value) |> printp()`).

In summary, as MT proficiency increased, ratings for CSE sentences also increased for both Chinese and Malay speakers. 
However, ratings for SSE sentences increased for Chinese speakers but _decreased_ for Malay speakers as MT proficiency increased.
