# Results

## Copular constructions

```{r data, include=F}
data_df <- read_csv(here("data", "data.csv")) #, locale = locale(encoding = "UTF-16LE"))
questions <- read_csv(here("data", "questions.csv"))

data_tib <- data_df |> 
  filter(Finished == "TRUE") |> 
  pivot_longer(cols = Q3_1:Q11_24, names_to = "question") |> 
  filter(!is.na(value)) |> 
  left_join(questions, by = "question") |> 
  mutate(q_type = q_type |> as.factor(),
         lang_group = lang_group |> as.factor(),
         value = value |> as.numeric(),
         proficiency = Q18 |> as.numeric())
```

```{r copula}
cop <- data_tib |> 
  filter(lang_group != 'O',
         test_phen == 1) |> 
  mutate(cop_type = cop_type |> as.factor() |> 
           fct_shift(1) |> `contrasts<-`(value = contr.sum(3) * 0.5),
         q_type = q_type |> fct_drop() |> `contrasts<-`(value = contr.sum(2) * 0.5),
         lang_group = lang_group |> fct_drop() |> `contrasts<-`(value = contr.sum(2) * 0.5))

cop_lm <- lmer(value ~ cop_type * q_type * lang_group + 
                 (1 | ResponseId) + (1 | s_label),
               data = cop)

cop_sum <- cop_lm |> tidy()
```

(ref:cop-plot) Distributions of ratings for copular constructions by complement type, sentence version, and language group. Black dashed lines indicate means. C: Chinese; M: Malay.
```{r cop-plot, out.width="100%", fig.cap="(ref:cop-plot)"}
cop_mean <- cop |> 
  group_by(cop_type, s_variant) |> 
  summarise(mean = mean(value),
            sd = sd(value),
            count = n()) |> 
  mutate(se = sd / sqrt(count),
         lower_ci = mean - se,
         upper_ci = mean + se)

cop_lab <- labeller(
  s_variant = c("a" = "With copula", "b" = "Without copula"), 
  cop_type = c(`1` = "NP", `2` = "AP", `3` = "PP"))

cop_plot <- ggplot(data = cop |> mutate(cop_type = cop_type |> 
                              fct_relevel(c("1", "2", "3")))) +
  geom_bar(aes(x = value, fill = lang_group), stat = "count") +
  geom_vline(aes(xintercept = mean), data = cop_mean, lty = "dashed") +
  facet_grid(cop_type ~ s_variant, labeller = cop_lab) +
  labs(x = "Rating", y = "Count") +
  scale_fill_brewer(palette = "Set2", name = "MT")

cop_plot
```

```{r cop_stats}
cop_sw <- cop_lm |> compute_redres() |> shapiro.test()
cop_emm_qt <- emmeans(cop_lm, ~ q_type) |> tidy()
cop_emm_cqt <- emmeans(cop_lm, ~ cop_type | q_type)
cop_con_cqt <- contrast(cop_emm_cqt, method = "pairwise") |> tidy()
cop_emm_cqt <- cop_emm_cqt |> tidy()
cop_emm_lg <- emmeans(cop_lm, ~ lang_group) |> tidy()
```

Participants' ratings for items involving copular constructions are shown in Figure \@ref(fig:cop-plot).
We conducted a linear regression with rating as the outcome variable, and complement type, sentence version, and MT as fixed effects with sum contrasts, along with all interactions. 
We also included participant and item as random effects.
The full model specification is as follows: `rating ~ comp_type * sent_version * mt + (1 | ppt_id) + (1 | item_id)`.[^03-01]

[^03-01]: A Shapiro--Wilk test revealed that residuals of the linear regression were not normally distributed ($W =$ `r cop_sw$statistic`, $p < .001$). 
However, visual observation of the Q--Q plot suggested that the deviation was minor and only occurred near the top tail of the distribution, which was expected due to negative skew (`r skewness(cop$value)`) associated with a ceiling effect. 
As such, linear regression remained the analysis of choice.
```{r cop-resqq}
cop_resqq <- plot_resqq(cop_lm)
```

Model results suggested that there was an unsurprising main effect of sentence version ($b =$ `r cop_sum |> filter(term == "q_type1") |> pull(estimate)`, $p =$ `r cop_sum |> filter(term == "q_type1") |> pull(p.value)`), with sentences including the copula having higher mean ratings (`r cop_emm_qt |> filter(q_type == 1) |> pull(estimate)` $\pm$ `r cop_emm_qt |> filter(q_type == 1) |> pull(std.error)`) than sentences without the copula (`r cop_emm_qt |> filter(q_type == 2) |> pull(estimate)` $\pm$ `r cop_emm_qt |> filter(q_type == 2) |> pull(std.error)`).[^03-02]

[^03-02]: Reported values indicate estimated marginal means and their 95% confidence intervals.

There was no main effect of MT ($b =$ `r cop_sum |> filter(term == "lang_group1") |> pull(estimate)`, $p =$ `r cop_sum |> filter(term == "lang_group1") |> pull(p.value)`), suggesting that mean ratings did not differ between Chinese speakers (`r cop_emm_lg |> filter(lang_group == "C") |> pull(estimate)` $\pm$ `r cop_emm_lg |> filter(lang_group == "C") |> pull(std.error)`) and Malay speakers (`r cop_emm_lg |> filter(lang_group == "M") |> pull(estimate)` $\pm$ `r cop_emm_lg |> filter(lang_group == "C") |> pull(std.error)`).

However, there were interaction effects between complement type and question type, as shown in Figure \@ref(fig:cop-pairwise). 
Post-hoc pairwise comparisons using the Tukey method revealed that there were no significant pairwise contrasts for sentences including the copula (all $p >$ `r cop_con_cqt |> filter(q_type == 1) |> pull(adj.p.value) |> min() |> floor_dec(1)`). 
However, there were significant pairwise contrasts for sentences without the copula.
Sentences with a PP complement (`r cop_emm_cqt |> filter(q_type == 2, cop_type == 3) |> pull(estimate)` $\pm$ `r cop_emm_cqt |> filter(q_type == 2, cop_type == 3) |> pull(std.error)`) had higher ratings than sentences with an NP complement (`r cop_emm_cqt |> filter(q_type == 2, cop_type == 1) |> pull(estimate)` $\pm$ `r cop_emm_cqt |> filter(q_type == 2, cop_type == 1) |> pull(std.error)`, $b =$ `r cop_con_cqt |> filter(q_type == 2, contrast == "2 - 3") |> pull(estimate) |> abs()`, $p =$ `r cop_con_cqt |> filter(q_type == 2, contrast == "2 - 3") |> pull(adj.p.value)`) and also had higher ratings than sentences with an AP complement (`r cop_emm_cqt |> filter(q_type == 2, cop_type == 2) |> pull(estimate)` $\pm$ `r cop_emm_cqt |> filter(q_type == 2, cop_type == 2) |> pull(std.error)`, $b =$ `r cop_con_cqt |> filter(q_type == 2, contrast == "3 - 1") |> pull(estimate) |> abs()`, $p =$ `r cop_con_cqt |> filter(q_type == 2, contrast == "3 - 1") |> pull(adj.p.value)`). 
Sentences with an NP complement were not significantly different than sentences with an AP complement ($b =$ `r cop_con_cqt |> filter(q_type == 2, contrast == "2 - 1") |> pull(estimate) |> abs()`, $p =$ `r cop_con_cqt |> filter(q_type == 2, contrast == "2 - 1") |> pull(adj.p.value)`).

(ref:cop-pw) Mean ratings for copular constructions by complement type and sentence version. \*: $p < .05$, \*\*: $p < .01$.
```{r cop-pairwise, out.width="100%", fig.cap="(ref:cop-pw)"}
cop_emm <- emmeans(cop_lm, ~ cop_type | q_type)
cop_con <- contrast(cop_emm, method = "pairwise") |> 
  as_tibble() |>
  separate(contrast, c("g1", "g2"), " - ") |> 
  mutate(group1 = pmin(g1, g2),
         group2 = pmax(g1, g2),
         p.signif = cut(p.value,
                        breaks = c(-Inf, .0001, .001, .01, .05, .1, 1),
                        labels = c("****", "***", "**", "*", "ns", "ns"))) |> 
  select(-g1, -g2) |> 
  arrange(q_type, group2) |> 
  add_x_position(x = "cop_type", 
                 group = "q_type", 
                 dodge = 0.9)

cop_pw <- ggplot(data = cop_mean |> mutate(cop_type = cop_type |> 
                                             fct_relevel(c("1", "2", "3")) |> 
                                             fct_recode("NP" = "1", 
                                                        "AP" = "2",
                                                        "PP" = "3"))) +
  geom_col(aes(y = mean, x = cop_type, fill = s_variant),
           position = position_dodge()) +
  geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci, 
                    x = cop_type, group = s_variant),
                width = 0.3,
                position = position_dodge(width = 0.9)) +
  stat_pvalue_manual(cop_con,
                     y.position = 1.1 * max(cop_mean$mean),
                     step.increase = 0.2,
                     tip.length = 0.03,
                     hide.ns = T) +
  labs(x = "Complement type", y = "Mean rating") +
  scale_fill_manual(name = "Sentence type",
                    labels = c("With copula", "Without copula"),
                    values = c("lightsalmon", "lightslateblue"))

cop_pw
```

Surprisingly, there were no interaction effects involving MT. 
There was no interaction between language and complement type ($p >$ `r cop_sum |> filter(grepl("cop_type[12]:lang_group", term)) |> pull(p.value) |> min() |> floor_dec(1)`), or language and sentence version ($p =$ `r cop_sum |> filter(grepl("q_type1:lang_group", term)) |> pull(p.value) |> min() |> floor_dec(1)`), or language and both complement type and sentence version ($p >$ `r cop_sum |> filter(grepl("cop_type[12]:q_type1:lang_group", term)) |> pull(p.value) |> min() |> floor_dec(1)`).

## Past tense marking

```{r past}
past <- data_tib |> 
  filter(lang_group != 'O',
         test_phen == 2) |> 
  mutate(past_type = past_type |> as.factor() |> 
           fct_shift(1) |> `contrasts<-`(value = contr.sum(5) * 0.5),
         q_type = q_type |> fct_drop() |> `contrasts<-`(value = contr.sum(2) * 0.5),
         lang_group = lang_group |> fct_drop() |> `contrasts<-`(value = contr.sum(2) * 0.5))

past_lm <- lmer(value ~ past_type * q_type * lang_group + 
                 (1 | ResponseId) + (1 | s_label),
               data = past)

past_sum <- past_lm |> tidy()
```

(ref:past-plot) Distributions of ratings for past tense constructions by past tense marker, sentence version, and language group. Black dashed lines indicate means. C: Chinese; M: Malay.
```{r past-plot, out.width="100%", fig.cap="(ref:past-plot)"}
past_mean <- past |> 
  group_by(past_type, s_variant) |> 
  summarise(mean = mean(value),
            sd = sd(value),
            count = n()) |> 
  mutate(se = sd / sqrt(count),
         lower_ci = mean - se,
         upper_ci = mean + se)

past_lab <- labeller(
  s_variant = c("a" = "With past marking", "b" = "Without past marking"), 
  past_type = c(`1` = "Suppletion", `2` = "Vowel", `3` = "[t]/[d]",
                `4` = "[ɪd]", `5` = "Vwl + [t]/[d]"))

past_plot <- ggplot(data = past |> mutate(past_type = past_type |> 
                               fct_relevel(c("1", "5", "2", "4", "3")))) +
  geom_bar(aes(x = value, fill = lang_group), stat = "count") +
  geom_vline(aes(xintercept = mean), data = past_mean, lty = "dashed") +
  facet_grid(past_type ~ s_variant, labeller = past_lab) +
  labs(x = "Rating", y = "Count") +
  scale_fill_brewer(palette = "Set2", name = "MT")

past_plot
```

```{r past_stats}
past_sw <- past_lm |> compute_redres() |> shapiro.test()
past_emm_qt <- emmeans(cop_lm, ~ q_type) |> tidy()
past_emm_lqt <- emmeans(cop_lm, ~ lang_group | q_type)
past_con_lqt <- contrast(past_emm_lqt, method = "pairwise") |> tidy()
past_emm_lg <- emmeans(cop_lm, ~ lang_group) |> tidy()
```

Participants' ratings for items involving past tense constructions are shown in Figure \@ref(fig:past-plot). 
We conducted a linear regression with rating as the outcome variable, and past marking type, sentence version, and MT as fixed effects with sum contrasts, along with all interactions. 
We also included participant and item as random effects.
The full model specification is as follows: `rating ~ past_type * sent_version * mt + (1 | ppt_id) + (1 | item_id)`.[^03-03]

[^03-03]: Similar to the ratings for copular constructions, Shapiro--Wilk test revealed that residuals of the linear regression were not normally distributed ($W =$ `r past_sw$statistic`, $p < .001$). 
Again, visual observation of the Q--Q plot suggested that the deviation was minor and only occurred near the top tail of the distribution, which was expected due to negative skew (`r skewness(past$value)`) associated with a ceiling effect. 
As such, linear regression remained the analysis of choice.
```{r past-resqq}
past_resqq <- plot_resqq(past_lm)
```

Model results suggested that there was again a main effect of sentence version ($b =$ `r past_sum |> filter(term == "q_type1") |> pull(estimate)`, $p =$ `r past_sum |> filter(term == "q_type1") |> pull(p.value)`), with sentences including the copula having higher mean ratings (`r past_emm_qt |> filter(q_type == 1) |> pull(estimate)` $\pm$ `r past_emm_qt |> filter(q_type == 1) |> pull(std.error)`) than sentences without the copula (`r past_emm_qt |> filter(q_type == 2) |> pull(estimate)` $\pm$ `r past_emm_qt |> filter(q_type == 2) |> pull(std.error)`).

There was again no main effect of MT ($b =$ `r past_sum |> filter(term == "lang_group1") |> pull(estimate)`, $p =$ `r past_sum |> filter(term == "lang_group1") |> pull(p.value)`), suggesting that mean ratings did not differ between Chinese speakers (`r past_emm_lg |> filter(lang_group == "C") |> pull(estimate)` $\pm$ `r past_emm_lg |> filter(lang_group == "C") |> pull(std.error)`) and Malay speakers (`r past_emm_lg |> filter(lang_group == "M") |> pull(estimate)` $\pm$ `r past_emm_lg |> filter(lang_group == "C") |> pull(std.error)`).

In contrast with the pattern of results for copular constructions, there were no significant interaction effects between past marking type and sentence version (all $p >$ `r past_sum |> filter(grepl("past_type[1-4]:q_type1$", term)) |> pull(p.value) |> min() |> floor_dec(2)`).
There were also no significant interaction effects between past marking type and both question type and MT (all $p >$ `r past_sum |> filter(grepl("past_type[1-4]:q_type1:", term)) |> pull(p.value) |> min() |> floor_dec(2)`).

Conversely, there was a significant interaction effect between sentence version and MT ($b =$ `r past_sum |> filter(term == "q_type1:lang_group1") |> pull(estimate)`, $p =$ `r past_sum |> filter(term == "q_type1:lang_group1") |> pull(p.value)`), as shown in Figure \@ref(fig:past-pw). 
Post-hoc pairwise comparisons using the Tukey method did not reveal any simple effects of MT (all $p >$ `r past_con_lqt |> pull(p.value) |> min() |> floor_dec(1)`), suggesting that Chinese and Malay speakers did not differ in their ratings for either sentence version, although they differed in the _difference_ in ratings between sentences with and without past tense marking. 

```{r past-pairwise, eval=F}
past_emm <- emmeans(past_lm, ~ past_type | q_type)
past_con <- contrast(past_emm, method = "pairwise") |> 
  as_tibble() |>
  separate(contrast, c("g1", "g2"), " - ") |> 
  mutate(group1 = pmin(g1, g2),
         group2 = pmax(g1, g2),
         p.signif = cut(p.value,
                        breaks = c(-Inf, .0001, .001, .01, .05, .1, 1),
                        labels = c("****", "***", "**", "*", "ns", "ns"))) |> 
  select(-g1, -g2) |> 
  arrange(q_type, group2) |> 
  add_x_position(x = "past_type", 
                 group = "q_type", 
                 dodge = 0.9)

past_pw <- ggplot(data = past_mean |> mutate(past_type = past_type |> 
                                             fct_relevel(c("1", "5", "2", "4", "3")) |> 
                                             fct_recode("Suppletion" = "1", 
                                                        "Vowel" = "2",
                                                        "[t]/[d]" = "3",
                                                        "[ɪd]" = "4",
                                                        "Vwl + [t]/[d]" = "5"))) +
  geom_col(aes(y = mean, x = past_type, fill = s_variant),
           position = position_dodge()) +
  geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci, 
                    x = past_type, group = s_variant),
                width = 0.3,
                position = position_dodge(width = 0.9)) +
  stat_pvalue_manual(past_con,
                     y.position = 1.1 * max(past_mean$mean),
                     step.increase = 0.2,
                     tip.length = 0.03,
                     hide.ns = T) +
  labs(x = "Past type", y = "Mean rating") +
  scale_fill_manual(name = "Sentence type",
                    labels = c("With past marking", "Without past marking"),
                    values = c("lightsalmon", "lightslateblue"))
```

(ref:past-pw) Mean ratings for past tense constructions by MT and sentence version. 
```{r past-pw, out.width="100%", fig.cap="(ref:past-pw)"}
past_mean_2 <- past |> 
  group_by(lang_group, s_variant) |> 
  summarise(mean = mean(value),
            sd = sd(value),
            count = n()) |> 
  mutate(se = sd / sqrt(count),
         lower_ci = mean - se,
         upper_ci = mean + se)

past_lm_2 <- lmer(value ~ q_type * lang_group + 
                    (1 | ResponseId) + (1 | s_label),
                  data = past)
past_emm_2 <- emmeans(past_lm_2, ~ lang_group | q_type)
past_con_2 <- contrast(past_emm_2, method = "pairwise") |> 
  as_tibble() |>
  separate(contrast, c("group1", "group2"), " - ") |> 
  mutate(p.signif = cut(p.value,
                        breaks = c(-Inf, .0001, .001, .01, .05, .1, 1),
                        labels = c("****", "***", "**", "*", "ns", "ns"))) # |> 
  # arrange(q_type, group2)# |> 
  #add_x_position(x = "past_type", 
                 # group = "q_type", 
                 # dodge = 0.9)

# doesn't work; need to redefine past_mean
past_pw_2 <- ggplot(data = past_mean_2) +
  geom_col(aes(y = mean, x = lang_group, fill = s_variant),
           position = position_dodge()) +
  geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci, 
                    x = lang_group, group = s_variant),
                width = 0.3,
                position = position_dodge(width = 0.9)) +
  stat_pvalue_manual(past_con_2,
                     y.position = 1.1 * max(past_mean_2$mean),
                     step.increase = 0.2,
                     tip.length = 0.03,
                     hide.ns = T) +
  labs(x = "Language group", y = "Mean rating") +
  scale_fill_manual(name = "Sentence type",
                    labels = c("With past marking", "Without past marking"),
                    values = c("lightsalmon", "lightslateblue"))

past_pw_2
```

## Individual differences

To better understand the observed variation in responses, we conducted two further exploratory analyses.
The first analysis involved understanding the relationship in participants' responses to the two types of constructions studied: were participants who rated CSE copula constructions more highly also more likely to rate CSE past tense constructions more highly?
We calculated the mean and 95% confidence intervals for both types of CSE constructions for each participant, shown in Figure \@ref(fig:cor).

(ref:cor) Ratings for copula and past tense CSE constructions by participant. Error bars indicate 95% confidence intervals.
```{r cor, out.width="100%", fig.cap="(ref:cor)"}
both <- data_tib |> 
  filter(lang_group != "O",
         q_type == 2) |> 
  group_by(ResponseId, test_phen) |> 
  summarise(avg_rating = mean(value),
            sd_rating = sd(value),
            n = n()) |> 
  mutate(se_rating = sd_rating / sqrt(n)) |> 
  select(-sd_rating, -n) |> 
  pivot_wider(names_from = test_phen,
              values_from = c(avg_rating, se_rating))

both_cor <- cor(both$avg_rating_1, both$avg_rating_2)

both_plot <- ggplot(both,
                    aes(x = avg_rating_1, y = avg_rating_2)) +
  geom_point() +
  geom_errorbar(aes(ymin = avg_rating_2 - 0.95*se_rating_2, 
                    ymax = avg_rating_2 + 0.95*se_rating_2),
                alpha = .5) +
  geom_errorbar(aes(xmin = avg_rating_1 - 0.95*se_rating_1, 
                    xmax = avg_rating_1 + 0.95*se_rating_1),
                alpha = .5) +
  geom_smooth(method = "lm") +
  geom_abline(slope = 1, intercept = 0, lty = "dashed") +
  labs(x = "Copula construction rating",
       y = "Past tense construction rating")
```

The correlation in means between the two types of CSE constructions was moderate, $r =$ `r both_cor`, suggesting that participants sometimes (but not always) endorsed both types of CSE constructions with similar ratings.
Additionally, many of the points lay above the $y = x$ line, suggesting that participants generally rated the CSE past tense constructions higher than the CSE copula constructions.

The second analysis studied the relationship between participants' ratings and their self-assessed MT language proficiency.
A histogram of participants' MT proficiencies is shown in Figure \@ref(fig:prof)

(ref:prof): Histogram of participants' self-assess MT language proficiency by language group.
```{r prof, out.width="100%", fig.cap="(ref:prof)"}
ppts <- data_tib |> 
  filter(lang_group != "O") |> 
  select(ResponseId, lang_group, proficiency) |> 
  distinct()

prof_plot <- ggplot(ppts, aes(x = proficiency)) + 
  geom_bar(aes(fill = lang_group), position = "dodge") +
  scale_fill_brewer(palette = "Set2", name = "MT") +
  labs(x = "MT proficiency",
       y = "Number of participants")
```

As the sample size did not support running a full statistical model with all levels of interaction, we omitted copula or past tense type as predictors, and instead ran a single joint model on both constructions.
We conducted a linear regression with rating as the outcome variable, and construction, sentence version, MT, and MT proficiency as fixed effects, along with all interactions. 
Construction, sentence version, and MT were coded with sum contrasts, and MT proficiency was standardised. 
We also included participant and item as random effects.


```{r prof}
by_prof <- data_tib |> 
  filter(lang_group != "O",
         test_phen %in% c(1, 2)) |> 
  mutate(test_phen = test_phen |> as.factor() |> `contrasts<-`(value = contr.sum(2) * 0.5),
         q_type = q_type |> fct_drop() |> `contrasts<-`(value = contr.sum(2) * 0.5),
         lang_group = lang_group |> fct_drop() |> `contrasts<-`(value = contr.sum(2) * 0.5),
         proficiency = proficiency |> scale())

prof_lm <- lmer(value ~ test_phen * q_type * lang_group * proficiency + 
          (1 | ResponseId) + (1 | s_label),
      data = by_prof)

cop_prof <- lmer(value ~ q_type * lang_group * proficiency + 
          (1 | ResponseId) + (1 | s_label),
      data = cop)

# cop_prof_b <- brm(value ~ cop_type * q_type * lang_group * proficiency + 
#           (1 | ResponseId) + (1 | s_label),
#       data = cop,
#       cores = 4,
#       prior = c(set_prior("normal(0,1)", class = "b")))
# note: multicollinearity between cop_type and proficiency 

# proficiency by rating
cop_prof_plot <- ggplot(cop, aes(x = proficiency, y = value)) + 
  geom_jitter(aes(shape = q_type, col = lang_group)) + 
  geom_smooth(aes(lty = q_type, col = lang_group), method = "lm")

past_prof <- lmer(value ~ past_type * q_type * lang_group * proficiency + 
          (1 | ResponseId) + (1 | s_label),
      data = past)

# proficiency by rating
past_prof_plot <- ggplot(past, aes(x = proficiency, y = value)) + 
  geom_jitter(aes(shape = q_type, col = lang_group)) + 
  geom_smooth(aes(lty = q_type, col = lang_group), method = "lm")

# past_prof_b <- brm(value ~ past_type * q_type * lang_group * proficiency + 
#           (1 | ResponseId) + (1 | s_label),
#       data = past,
#       cores = 4,
#       prior = c(set_prior("normal(0,1)", class = "b")))

```
