# Appendix: Questionnaire

This appendix contains the full list of sentences used in the acceptability judgement task, the rating scale, as well as the demographic questions presented to participants.

## Acceptability judgement items {#sec:items}
The items used in the acceptability judgement task are shown in Table \@ref(tab:qn-acc).
Words in braces indicate alternations between SSE versions (before the slash) and CSE versions (after the slash) of the sentence.

```{r qn-acc}
q_items <- read_csv("data/questionnaire_items.csv")
q_items |> 
  gt(caption = "Items for acceptability judgement task.") |> 
  fmt_markdown(columns = Sentence) |> 
  tab_options(table.width = pct(100),
              latex.use_longtable = TRUE) |> 
  cols_align(
    align = "right",
    columns = "No."
  )
```

\newpage

## Rating scale {#sec:scale}
The scale that participants were asked to use for ratings is shown in Table \@ref(tab:qn-scale).
```{r qn-scale}
q_scale <- read_csv("data/questionnaire_scale.csv")
q_scale |> 
  gt(caption = "Rating scale for acceptability judgement task.") |> 
  tab_options(table.width = pct(100),
              latex.use_longtable = TRUE) |> 
  cols_width(Description ~ pct(92))
```

\newpage 

## Demographic questions {#sec:demogs}
The demographic questions presented to participants are shown in Table \@ref(tab:qn-demog).
Some of the questions required participants to select an option; in these cases, the possible options are listed in brackets.

```{r qn-demog}
q_demogs <- read_csv("data/questionnaire_demogs.csv",
                     col_types = "cc")
q_demogs |> 
  gt(caption = "Demographic questions.") |> 
  tab_options(table.width = pct(100),
              latex.use_longtable = TRUE) |> 
  cols_width(Question ~ pct(95))
```

